STAT 450 Project: Real Estate

### 2020-03-31 src/2nd_draft.Rmd
finalized

---
title: 'STAT 450 Project: Real Estate'
author: "Xuechun Lu, Yuting Wen, Peter Han, Yuetong Liu"
date: "15/03/2020"
output:
  pdf_document
---

@@

Model | PMSE:Min | PMSE:Mean | PMSE:Max
-----|-----|-----|-----|
Full Model | 5.23 | 5.43 | 5.52 |
Transformed Model | 4.45 | 4.59 | 4.64 |
Null Model | 36.33 | 36.52 | 36.64 |
The Lasso for Full Model | 4.52 | 4.63 | 4.73 |
Ridge Regression for Full Model | 4.50 | 4.63 | 4.72 |

@@

Model | PMSE:Min | PMSE:Mean | PMSE:Max
-----|-----|-----|-----|
Full Model | 6.50 | 6.97 | 7.59 |
Transformed Model | 5.60 | 5.92 | 6.51 |
Null Model | 36.67 | 36.87 | 37.26 |
The Lasso for Full Model | 5.58 | 5.91 | 6.40 |
Ridge Regression for Full Model | 5.53 | 5.88 | 6.39 |

>>>>

---
title: 'STAT 450 Project: Real Estate'
author: "Peter Han, Xuechun Lu, Yuetong Liu, Yuting Wen"
date: "30/03/2020"
output:
  pdf_document
---

@@

Model | PMSE:Min | PMSE:Mean | PMSE:Max
-----|-----|-----|-----|
Full Model | 5.23 | 5.43 | 5.52 |
Transformed Model | 4.45 | 4.59 | 4.64 |
Null Model | 36.33 | 36.52 | 36.64 |
Lasso for Full Model | 4.52 | 4.63 | 4.73 |
Ridge Regression for Full Model | 4.50 | 4.63 | 4.72 |

@@

Model | PMSE:Min | PMSE:Mean | PMSE:Max
-----|-----|-----|-----|
Full Model | 6.50 | 6.97 | 7.59 |
Transformed Model | 5.60 | 5.92 | 6.51 |
Null Model | 36.67 | 36.87 | 37.26 |
Lasso for Full Model | 5.58 | 5.91 | 6.40 |
Ridge Regression for Full Model | 5.53 | 5.88 | 6.39 |
